Software Citation Principles

### 2016-03-31 sc-principles/software-citation-principles.tex
small changes to text in 4

In astronomy \& astrophysics: The Astronomy Source Code Library
(ASCL)~\cite{ascl}, is a website dedicated to the curation and indexing of
software used in the astronomy-based literature. In 2015, the AAS and GitHub
co-hosted a workshop~\cite{aas-software-index} dedicated to software citation,
indexing and discoverability and more recently, a Birds of a Feather session
was held at the Astronomical Data Analysis Software and Systems (ADASS) XXV
conference~\cite{2015arXiv151207919A} which included discussion of software
citation.

The life sciences: In May 2014, the NIH held a workshop aimed at helping the biomedical community discover, cite and reuse software written by their peers. The primary outcome of this workshop was the Software Discovery Index Meeting Report~\cite{software-discovery-index}. The authors of the report cite discuss what framework would be required for supporting a Software Discovery Index including the need for unique identifiers, how citations to these would be handled by publishers and the critical need for metadata to describe software packages.

Geosciences: The Ontosoft~\cite{ontosoft} project describes itself as `A Community Software Commons for the Geosciences'. Lots of attention given to the metadata
required to describe, discover and execute research software. NSF geosciences workshop around data lifecycle, management and citation~\cite{nsf-geo-data}. This report includes many recommendations for data citation.
\LJHnote{ The Seismological Research Letters, Electronic Seismologists publishes papers on software.} %text needs to be cleaned up LJH%

>>>>

In astronomy and astrophysics: The Astronomy Source Code Library
(ASCL)~\cite{ascl}, is a website dedicated to the curation and indexing of
software used in the astronomy-based literature. In 2015, the AAS and GitHub
co-hosted a workshop~\cite{aas-software-index} dedicated to software citation,
indexing and discoverability and more recently, a Birds of a Feather session
was held at the Astronomical Data Analysis Software and Systems (ADASS) XXV
conference~\cite{2015arXiv151207919A} which included discussion of software
citation.

In the life sciences: In May 2014, the NIH held a workshop aimed at helping the biomedical community discover, cite and reuse software written by their peers. The primary outcome of this workshop was the Software Discovery Index Meeting Report~\cite{software-discovery-index}. The authors of the report cite discuss what framework would be required for supporting a Software Discovery Index including the need for unique identifiers, how citations to these would be handled by publishers and the critical need for metadata to describe software packages.

In the geosciences: The Ontosoft~\cite{ontosoft} project describes itself as `A Community Software Commons for the Geosciences'. Lots of attention given to the metadata
required to describe, discover and execute research software. NSF geosciences workshop around data lifecycle, management and citation~\cite{nsf-geo-data}. This report includes many recommendations for data citation.
\LJHnote{ The Seismological Research Letters, Electronic Seismologists publishes papers on software.} %text needs to be cleaned up LJH%
